Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
remove levels table
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@724 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsubsection{Experiment with three factors}
The first experiment that was done, was the experiment with only three
factors. The goal here was to see how the ontologies behave with a
small amount of querying and factors.  Table \ref{facandlevExp1} show
the different factors and their levels. We chose to start with a small
experiment using only simple factors which had few possible
values. That is why we chose transmission and fuel type as factors as
well as the ontology factor. With these three factors we got $2^3$
number of runs. This experiment was also replicated four times to get the
most accurate results.  The results were calculated by finding the
average response time for each run between all four replications.

\begin{wraptable}{l}{0.67\textwidth}
    \begin{tabular}{ | l | l l |}
    \hline
    {\bf Factor} & {\bf Level 1} & {\bf Level 2} \\ \hline
	Ontology & -vso & -co \\ \hline 
	Fuel type & Diesel & Unleaded Petrol \\ \hline 
	Transmission & Manual Gearbox & Automatic Gearbox \\ \hline 
    \end{tabular}
\caption{Factors and levels for experiment 1}\label{facandlevExp1}
\end{wraptable}

The next step was to create the planning matrix for this
experiment. Table
\ref{3factor} shows all the 8 runs for the experiment with three
factors. We also ran a randomized version the experiment to check
whether the randomization would influence the experiment. The results
were almost equal which eliminated randomization as a factor.  Both
results can be found in appendix \ref{appD}. After each run the
response time were logged to that particular run. The response time
were then used to check for significant effect when the experiment
were evaluated
\begin{wraptable}{l}{0.67\textwidth}
    \begin{tabular}{ | l | l l l |}
    \hline
    {\bf Run} & {\bf Ontology} & {\bf Fuel type} & {\bf Transmission} \\ \hline
	1 & -vso & Diesel & Automatic Gearbox \\ \hline 
	2 & -co & Diesel & Automatic Gearbox \\ \hline 
	3 & -vso & Unleaded Petrol & Automatic Gearbox \\ \hline 
	4 & -co & Unleaded Petrol & Automatic Gearbox \\ \hline 
	5 & -vso & Diesel & Manual Gearbox \\ \hline 
	6 & -co & Diesel & Manual Gearbox \\ \hline 
	7 & -vso & Unleaded Petrol & Manual Gearbox \\ \hline 
	8 & -co & Unleaded Petrol & Manual Gearbox \\ \hline 
    \end{tabular}
\caption{Planning matrix for experiment with three factors}\label{3factor}
\end{wraptable}

>>>>

\subsubsection{Experiment with three factors}
We first made a very simple three factor experiment. The main goal here was
to see how the ontologies behave with a small amount of querying and
factors. We chose to start with a small experiment using only
simple factors which had few possible values. That is why we chose
transmission and fuel type as factors as well as the ontology
factor. With these three factors we got $2^3$ number of runs. This
experiment was also replicated four times to get the most accurate
results.  The results were calculated by finding the average response
time for each run between all four replications.

The next step was to create the planning matrix for this
experiment. Table \ref{3factor} shows all the 8 runs for the
experiment with three factors.  After each run the response time were
logged to that particular run. The response time were then used to
check for significant effect when the experiment were evaluated
\begin{wraptable}{l}{0.67\textwidth}
    \begin{tabular}{ | l | l l l |}
    \hline
    {\bf Run} & {\bf Ontology} & {\bf Fuel type} & {\bf Transmission} \\ \hline
	1 & -vso & Diesel & Automatic Gearbox \\ \hline 
	2 & -co & Diesel & Automatic Gearbox \\ \hline 
	3 & -vso & Unleaded Petrol & Automatic Gearbox \\ \hline 
	4 & -co & Unleaded Petrol & Automatic Gearbox \\ \hline 
	5 & -vso & Diesel & Manual Gearbox \\ \hline 
	6 & -co & Diesel & Manual Gearbox \\ \hline 
	7 & -vso & Unleaded Petrol & Manual Gearbox \\ \hline 
	8 & -co & Unleaded Petrol & Manual Gearbox \\ \hline 
    \end{tabular}
    \caption{Planning matrix for experiment with three factors and
      their levels.}\label{3factor}
\end{wraptable}
